---
title: "Index Market Analysis Report"
subtitle: "Comparative Analysis of Asian and European Markets"
author: "S.Matsumoto"
date: "2024-10-28"
format:
  revealjs:
    theme:
      - custom.scss
      - brand
    transition: slide
    slide-number: true
    footer: "Market Analysis 2024"
    self-contained: true
execute:
  echo: false
  warning: false
  message: false

---

```{r setup, include=FALSE}
# Load necessary libraries
library(tidyverse)
library(ggplot2)
library(plotly)
library(DT)
library(knitr)
library(patchwork)
library(scales)
library(viridis)
library(corrplot)
library(kableExtra)
```

```{r load_data}
# Load the CSV files
all_asian_comparisons <- read.csv("data/all_asian_comparisons.csv", stringsAsFactors = FALSE)
all_european_comparisons <- read.csv("data/all_european_comparisons.csv", stringsAsFactors = FALSE)
asia_europe_comparison <- read.csv("data/asia_europe_comparison.csv", stringsAsFactors = FALSE)
countrybenchmarkcomparisons <- read.csv("data/country-benchmark-comparisons.csv", stringsAsFactors = FALSE)
outperformance_summary_euro_asia <- read.csv("data/outperformance_summary_euro_asia.csv", stringsAsFactors = FALSE)
outperformance_summary <- read.csv("data/outperformance-summary.csv", stringsAsFactors = FALSE)

# Combine Asian and European data
all_comparisons <- rbind(all_asian_comparisons, all_european_comparisons)

# Remove Saudi Arabia as specified in the instructions
all_comparisons <- all_comparisons %>% filter(country != "Saudiarabia")
outperformance_summary <- outperformance_summary %>% filter(country != "Saudiarabia")
outperformance_summary_euro_asia <- outperformance_summary_euro_asia %>% filter(country != "Saudiarabia")
```

## Introduction

This analysis explores investment opportunities across Asian and
European markets, focusing on:

1.  Identifying **stable markets** for consistent profits
2.  Finding **high-return countries** for growth investment
3.  Determining **markets to avoid**
4.  Comparing investment attractiveness between **Asia** and **Europe**

## Executive Summary

Our analysis reveals several key insights:

-   **Most stable markets:** India, Indonesia, and Singapore
-   **Highest returning markets:** India, Indonesia, and Germany
-   **Markets to avoid:** Italy, Spain, and France
-   **Regional comparison:** Asian markets show higher returns with
    higher volatility, while European markets (Germany, Netherlands)
    demonstrate more consistent performance

## 1. Market Stability Analysis {.section .center}

::: notes
The first section focuses on which markets provide the most stable
returns.
:::

## Market Stability Metrics

```{r}
# Calculate stability metrics for each country
stability_metrics <- all_comparisons %>%
  group_by(country, benchmark) %>%
  summarize(
    mean_return = mean(country_return, na.rm = TRUE),
    std_dev = sd(country_return, na.rm = TRUE),
    coef_variation = std_dev / abs(mean_return),  # coefficient, lower values indicate more stable returns relative to the average return.
    sharpe_ratio = mean_return / std_dev,
    pos_years_pct = mean(country_return > 0, na.rm = TRUE) * 100,
    n_years = n(),
    .groups = 'drop'
  ) %>%
  arrange(desc(sharpe_ratio))

# Create a table of stability metrics
stability_metrics %>%
  head(6) %>%
  mutate(
    mean_return = sprintf("%.2f%%", mean_return),
    std_dev = sprintf("%.2f%%", std_dev),
    coef_variation = round(coef_variation, 2),# coefficient of variation
    sharpe_ratio = round(sharpe_ratio, 3),
    pos_years_pct = sprintf("%.1f%%", pos_years_pct)
  ) %>%
  select(country, mean_return, std_dev, sharpe_ratio, pos_years_pct) %>%
  kable(
    caption = "Top Markets by Stability Metrics",
    col.names = c("Country", "Mean Return", "Std Dev", "Sharpe Ratio", "% Positive Years"),
    align = "lrrrr"
  )
```

## Sharp Return

**Higher values are better**: A higher Sharpe ratio indicates better
risk-adjusted performance

|                      |                                         |
|----------------------|-----------------------------------------|
| Sharpe ratio \< 1.0: | Poor risk-adjusted return               |
| Sharpe ratio 1.0-2.0 | Acceptable to good risk-adjusted return |
| Sharpe ratio \> 2.0: | Excellent risk-adjusted return          |

## Risk-Return Analysis

```{r}
# Create a risk-return plot
ggplot(stability_metrics, aes(x = std_dev, y = mean_return, size = sharpe_ratio,
                             color = factor(ifelse(country %in% c("India", "Indonesia", "Germany", "China", "South Korea"), country, "Other")))) +
  geom_point(alpha = 0.7) +
  geom_text(aes(label = country), hjust = -0.2, vjust = 0, size = 3) +
  scale_color_manual(values = c("India" = "#FF9933", "Indonesia" = "#FF0000", "Germany" = "#000000", 
                               "China" = "#DE2910", "South Korea" = "#003478", "Other" = "#999999")) +
  labs(
    title = "Risk vs. Return by Country",
    x = "Risk (Standard Deviation of Returns, %)",
    y = "Average Annual Return (%)",
    color = "Country"
  ) +
  theme_minimal() +
  # Add reference lines for the average risk and return
  geom_hline(yintercept = mean(stability_metrics$mean_return), linetype = "dashed", alpha = 0.5) +
  geom_vline(xintercept = mean(stability_metrics$std_dev), linetype = "dashed", alpha = 0.5)
```

## Market Consistency

```{r}
# Calculate positive and negative year streaks
streak_analysis <- function(returns) {
  current_streak <- 0
  current_sign <- NA
  pos_streaks <- c()
  neg_streaks <- c()
  
  for (ret in returns) {
    sign <- ret >= 0
    if (is.na(current_sign)) {
      current_sign <- sign
      current_streak <- 1
    } else if (sign == current_sign) {
      current_streak <- current_streak + 1
    } else {
      if (current_sign) {
        pos_streaks <- c(pos_streaks, current_streak)
      } else {
        neg_streaks <- c(neg_streaks, current_streak)
      }
      current_sign <- sign
      current_streak <- 1
    }
  }
  
  # Add the final streak
  if (!is.na(current_sign)) {
    if (current_sign) {
      pos_streaks <- c(pos_streaks, current_streak)
    } else {
      neg_streaks <- c(neg_streaks, current_streak)
    }
  }
  
  list(
    max_pos_streak = if (length(pos_streaks) > 0) max(pos_streaks) else 0,
    max_neg_streak = if (length(neg_streaks) > 0) max(neg_streaks) else 0
  )
}
# Calculate streak metrics
streak_metrics <- all_comparisons %>%
  group_by(country) %>%
  arrange(country, year) %>%
  summarize(
    returns = list(country_return),
    .groups = 'drop'
  ) %>%
  rowwise() %>%
  mutate(
    streaks = list(streak_analysis(returns)),
    max_pos_streak = streaks$max_pos_streak,
    max_neg_streak = streaks$max_neg_streak
  ) %>%
  select(country, max_pos_streak, max_neg_streak)

# Join with stability metrics
consistency_metrics <- stability_metrics %>%
  left_join(streak_metrics, by = "country") %>%
  arrange(desc(pos_years_pct))

# Visualize consistency
consistency_metrics %>%
  arrange(desc(pos_years_pct)) %>%
  head(10) %>%
ggplot(aes(x = reorder(country, pos_years_pct), y = pos_years_pct, 
                                fill = ifelse(max_pos_streak >= 3, "High", "Moderate"))) +
  geom_col() +
  geom_text(aes(label = sprintf("%.0f%%", pos_years_pct)), hjust = -0.1) +
  scale_fill_manual(values = c("High" = "#4CAF50", "Moderate" = "#81C784")) +
  coord_flip() +
  labs(
    title = "Market Consistency Analysis",
    subtitle = "Percentage of years with positive returns",
    x = "",
    y = "Percentage of Years with Positive Returns",
    fill = "Consistency Level"
  ) +
  theme_minimal() +
  theme(legend.position = "bottom")
```

## 2. High-Return Markets Analysis {.section .center}

::: notes
The second section identifies markets with the highest returns.
:::

## Top Performing Markets

```{r}
# Sort by mean return (descending)
ggplot(stability_metrics, aes(x = reorder(country, mean_return), y = mean_return, 
                             fill = ifelse(country %in% head(arrange(stability_metrics, desc(mean_return)), 5)$country, "Top", "Other"))) +
  geom_col() +
  geom_text(aes(label = sprintf("%.1f%%", mean_return)), hjust = -0.1) +
  scale_fill_manual(values = c("Top" = "#FFC107", "Other" = "#FFECB3")) +
  coord_flip() +
  labs(
    title = "Average Annual Returns by Country",
    x = "",
    y = "Average Annual Return (%)"
  ) +
  theme_minimal() +
  theme(legend.position = "none")
```

## Annual Returns of Top Performers

```{r}
# Get top 5 performing markets
high_return_markets <- stability_metrics %>%
  arrange(desc(mean_return)) %>%
  head(5)

# Plot yearly returns of top performers
all_comparisons %>%
  filter(country %in% high_return_markets$country) %>%
  ggplot(aes(x = year, y = country_return, color = country, group = country)) +
  geom_line(linewidth = 1) +
  geom_point() +
  theme_minimal() +
  labs(
    title = "Annual Returns of Top-Performing Markets",
    x = "Year",
    y = "Annual Return (%)",
    color = "Country"
  ) +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom")
```

## 3. Markets to Avoid {.section .center}

::: notes
The third section identifies markets that investors should avoid.
:::

## Poor Risk-Adjusted Returns

```{r}
# Identify markets with poor risk-adjusted returns
markets_to_avoid <- stability_metrics %>%
  arrange(sharpe_ratio) %>%
  head(5)

# Visualize markets to avoid
ggplot(stability_metrics, aes(x = reorder(country, -sharpe_ratio), y = sharpe_ratio, 
                             fill = ifelse(country %in% markets_to_avoid$country, "Bottom", "Other"))) +
  geom_col() +
  geom_text(aes(label = sprintf("%.3f", sharpe_ratio)), vjust = -0.3) +
  scale_fill_manual(values = c("Bottom" = "#F44336", "Other" = "#FFCDD2")) +
  labs(
    title = "Risk-Adjusted Returns (Sharpe Ratio) by Country",
    subtitle = "Lower values indicate poor risk-reward tradeoff",
    x = "Country",
    y = "Sharpe Ratio (Return/Risk)"
  ) +
  theme_minimal() +
  theme(
    legend.position = "none",
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
```

## Market Evaluation Framework

```{r}
mean_sharpe <- mean(stability_metrics$sharpe_ratio)
mean_pos_years <- mean(stability_metrics$pos_years_pct)

ggplot(stability_metrics, aes(x = sharpe_ratio, y = pos_years_pct, color = factor(ifelse(country %in% markets_to_avoid$country, "Avoid", "Consider")))) +
  geom_point(size = 3) +
  geom_text(aes(label = country), hjust = -0.2, vjust = 0, size = 3) +
  scale_color_manual(values = c("Avoid" = "#F44336", "Consider" = "#4CAF50")) +
  geom_hline(yintercept = mean_pos_years, linetype = "dashed", alpha = 0.5) +
  geom_vline(xintercept = mean_sharpe, linetype = "dashed", alpha = 0.5) +
  annotate("rect", xmin = min(stability_metrics$sharpe_ratio), xmax = mean_sharpe,
           ymin = min(stability_metrics$pos_years_pct), ymax = mean_pos_years,
           alpha = 0.1, fill = "red") +
  annotate("text", x = min(stability_metrics$sharpe_ratio) + (mean_sharpe - min(stability_metrics$sharpe_ratio))/2,
           y = min(stability_metrics$pos_years_pct) + (mean_pos_years - min(stability_metrics$pos_years_pct))/2,
           label = "AVOID", color = "red", size = 5, alpha = 0.7) +
  labs(
    title = "Market Evaluation Framework",
    subtitle = "Markets in the bottom-left quadrant should be avoided",
    x = "Risk-Adjusted Return (Sharpe Ratio)",
    y = "Consistency (% Positive Years)",
    color = "Recommendation"
  ) +
  theme_minimal() +
  theme(legend.position = "bottom")
```

## 4. Regional Comparison: Asia vs. Europe {.section .center}

::: notes
The fourth section compares Asian and European markets.
:::

## Performance Comparison: Asia vs. Europe

```{r}
# Calculate regional performance metrics
regional_metrics <- all_comparisons %>%
  group_by(benchmark) %>%
  summarize(
    mean_return = mean(country_return, na.rm = TRUE),
    median_return = median(country_return, na.rm = TRUE),
    std_dev = sd(country_return, na.rm = TRUE),
    sharpe_ratio = mean_return / std_dev,
    pos_years_pct = mean(country_return > 0, na.rm = TRUE) * 100,
    outperformance_rate = mean(outperformed, na.rm = TRUE) * 100,
    .groups = 'drop'
  )

# Display regional metrics
regional_metrics %>%
  filter(benchmark %in% c("Asia8", "Euro7")) %>%
  mutate(
    mean_return = sprintf("%.2f%%", mean_return),
    median_return = sprintf("%.2f%%", median_return),
    std_dev = sprintf("%.2f%%", std_dev),
    sharpe_ratio = round(sharpe_ratio, 3),
    pos_years_pct = sprintf("%.1f%%", pos_years_pct),
    outperformance_rate = sprintf("%.1f%%", outperformance_rate)
  ) %>%
  kable(
    caption = "Performance Comparison: Asia vs. Europe",
    col.names = c("Region", "Mean Return", "Median Return", "Std Dev", "Sharpe Ratio", 
                  "% Positive Years", "% Outperformance"),
    align = "lrrrrrr"
  )
```

## Regional Returns Over Time

```{r}
# Visual comparison of regions
regional_comparison <- all_comparisons %>%
  group_by(benchmark, year) %>%
  summarize(
    mean_return = mean(country_return, na.rm = TRUE),
    .groups = 'drop'
  )

# Plot regional returns over time
ggplot(regional_comparison %>% filter(benchmark %in% c("Asia8", "Euro7")), 
       aes(x = year, y = mean_return, color = benchmark, group = benchmark)) +
  geom_line(linewidth = 1) +
  geom_point() +
  theme_minimal() +
  labs(
    title = "Average Returns by Region Over Time",
    x = "Year",
    y = "Average Annual Return (%)",
    color = "Region"
  ) +
  scale_color_manual(values = c("Asia8" = "#FF9933", "Euro7" = "#003399")) +
  theme(legend.position = "bottom")
```

## Outperformance Analysis

```{r}
# Country-level outperformance visualization
ggplot(outperformance_summary_euro_asia, aes(x = reorder(country, pct_outperformed), 
                                         y = pct_outperformed, fill = benchmark)) +
  geom_col() +
  geom_text(aes(label = sprintf("%.1f%%", pct_outperformed)), hjust = -0.1) +
  scale_fill_manual(values = c("Asia8" = "#FF9933", "Euro7" = "#003399"),
                   labels = c("Asia8" = "Asia", "Euro7" = "Europe")) +
  coord_flip() +
  facet_grid(benchmark ~ ., scales = "free_y", space = "free_y") +
  labs(
    title = "Frequency of Outperformance vs Regional Benchmark",
    subtitle = "Percentage of years each country outperformed its regional benchmark",
    x = "",
    y = "Percentage of Years (%)"
  ) +
  theme_minimal() +
  theme(legend.position = "none") +
  ylim(0, 100)
```

## Return vs Outperformance

```{r}
# Join the stability metrics with outperformance data
performance_combined <- stability_metrics %>%
  left_join(
    outperformance_summary_euro_asia %>% 
      select(country, pct_outperformed, avg_outperformance),
    by = "country"
  ) %>%
  # Add region information
  mutate(benchmark = case_when(
    country %in% unique(all_asian_comparisons$country) ~ "Asia",
    country %in% unique(all_european_comparisons$country) ~ "Europe",
    TRUE ~ "Other"
  ))

# Plot correlation between returns and outperformance
ggplot(performance_combined, aes(x = mean_return, y = pct_outperformed, 
                                color = benchmark, size = sharpe_ratio)) +
  geom_point(alpha = 0.7) +
  geom_text(aes(label = country), hjust = -0.2, vjust = 0, size = 3) +
  scale_color_manual(values = c("Asia" = "#FF9933", "Europe" = "#003399")) +
  labs(
    title = "Relationship Between Returns and Benchmark Outperformance",
    x = "Average Annual Return (%)",
    y = "% of Years Outperforming Benchmark",
    color = "Region",
    size = "Sharpe Ratio"
  ) +
  theme_minimal() +
  theme(legend.position = "bottom")
```

## Performance Heatmap

```{r}
# Performance Heatmap
all_comparisons %>%
  ggplot(aes(x = year, y = country, fill = difference)) +
  geom_tile() +
  scale_fill_gradient2(
    low = "red", mid = "white", high = "green", 
    midpoint = 0, name = "Difference (%)"
  ) +
  facet_grid(benchmark ~ ., scales = "free_y", space = "free_y") +
  labs(
    title = "Country Performance vs Regional Benchmark",
    subtitle = "Green = outperformed benchmark, Red = underperformed benchmark",
    x = "Year",
    y = ""
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5))
```

## Return Distribution by Region

```{r}
# Create density plots for return distributions
ggplot(all_comparisons %>% filter(benchmark %in% c("Asia8", "Euro7")), 
       aes(x = country_return, fill = benchmark)) +
  geom_density(alpha = 0.5) +
  scale_fill_manual(values = c("Asia8" = "#FF9933", "Euro7" = "#003399")) +
  labs(
    title = "Distribution of Annual Returns by Region",
    x = "Annual Return (%)",
    y = "Density",
    fill = "Region"
  ) +
  theme_minimal() +
  theme(legend.position = "bottom")
```

## Market Correlations

```{r}

# Calculate correlation matrix of returns
country_returns <- all_comparisons %>%
  select(year, country, country_return) %>%
  pivot_wider(names_from = country, values_from = country_return)

# Convert to correlation matrix
corr_matrix <- country_returns %>%
  select(-year) %>%
  cor(use = "pairwise.complete.obs")

# Add region information
country_regions <- all_comparisons %>%
  select(country, benchmark) %>%
  distinct()


# Order countries by region
ordered_countries <- country_regions %>%
  arrange(benchmark, country) %>%
  pull(country)

# Create a dataframe for plotting
corr_df <- as.data.frame(as.table(corr_matrix))
names(corr_df) <- c("Country1", "Country2", "Correlation")
# Create correlation heatmap
corr_df %>%
  filter(Country1 %in% high_return_markets$country | Country2 %in% high_return_markets$country) %>%
  ggplot(aes(x = factor(Country1, levels = ordered_countries), 
                    y = factor(Country2, levels = rev(ordered_countries)), 
                    fill = Correlation)) +
  geom_tile() +
  scale_fill_gradient2(low = "blue", mid = "white", high = "red", midpoint = 0,
                      limits = c(-1, 1)) +
  geom_text(aes(label = sprintf("%.2f", Correlation)), size = 2.5) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size = 8),
    axis.text.y = element_text(size = 8)
  ) +
  labs(
    title = "Correlation Matrix of Market Returns",
    subtitle = "Red indicates positive correlation, blue indicates negative correlation",
    x = NULL, y = NULL
  )
```

## Crisis Performance

```{r}
# Define crisis years
crisis_years <- c(2008, 2020)  # Global Financial Crisis, COVID-19 pandemic

# Calculate crisis performance
crisis_performance <- all_comparisons %>%
  filter(year %in% crisis_years) %>%
  mutate(crisis = ifelse(year == 2008, "2008 Financial Crisis", "2020 COVID-19")) %>%
  group_by(country, benchmark, crisis) %>%
  summarize(
    return = mean(country_return),
    .groups = 'drop'
  ) %>%
  arrange(crisis, return)

# Visualize crisis performance
ggplot(crisis_performance, aes(x = reorder(interaction(country, crisis), return), 
                               y = return, fill = benchmark)) +
  geom_col() +
  geom_text(aes(label = sprintf("%.1f%%", return)), 
            hjust = ifelse(crisis_performance$return < 0, 1.1, -0.1),
            color = ifelse(crisis_performance$return < 0, "white", "black"),
            size = 3) +
  scale_fill_manual(values = c("Asia8" = "#FF9933", "Euro7" = "#003399")) +
  coord_flip() +
  facet_wrap(~crisis, scales = "free_y") +
  theme_minimal() +
  labs(
    title = "Market Performance During Crisis Years",
    x = NULL,
    y = "Return (%)",
    fill = "Region"
  )+
  theme(
    legend.position = "top"
  )
```

## Risk-Return Efficiency

```{r}
# Create a risk-return plot with an efficiency frontier
ggplot(stability_metrics, aes(x = std_dev, y = mean_return)) +
  # Add points for each country
  geom_point(aes(color = factor(ifelse(country %in% c("India", "Indonesia", "Germany", "Italy", "Spain"), 
                                       country, "Other")),
                size = sharpe_ratio)) +
  # Add text labels for each country
  geom_text(aes(label = country), hjust = -0.2, vjust = 0, size = 3) +
  # Custom color scale
  scale_color_manual(values = c("India" = "#FF9933", "Indonesia" = "#FF0000", 
                              "Germany" = "#000000", "Italy" = "#008C45", 
                              "Spain" = "#AA151B", "Other" = "#999999")) +
  # Add a curve representing the theoretical efficiency frontier
  stat_function(fun = function(x) { 2 + 0.5 * x }, 
                linetype = "dashed", color = "darkblue") +
  # Add annotations
  annotate("text", x = max(stability_metrics$std_dev) * 0.8, 
           y = 2 + 0.5 * max(stability_metrics$std_dev) * 0.8,
           label = "Theoretical Efficiency Frontier", 
           color = "darkblue", angle = 20, size = 3) +
  # Customize theme
  theme_minimal() +
  # Add labels
  labs(
    title = "Risk-Return Efficiency Analysis",
    subtitle = "Markets closer to the frontier offer better risk-adjusted returns",
    x = "Risk (Standard Deviation, %)",
    y = "Return (%)",
    color = "Country",
    size = "Sharpe Ratio"
  ) +
  theme(legend.position = "bottom")
```

## Conclusion {.section .center}

::: notes
Final conclusions and investment recommendations.
:::

## Most Stable Markets

```{r}
# Calculate stability metrics for each country
stability_metrics <- all_comparisons %>%
  group_by(country, benchmark) %>%
  summarize(
    mean_return = mean(country_return, na.rm = TRUE),
    median_return = median(country_return, na.rm = TRUE),
    std_dev = sd(country_return, na.rm = TRUE),
    coef_variation = std_dev / abs(mean_return),  # Add coefficient of variation
    sharpe_ratio = mean_return / std_dev,
    pos_years_pct = mean(country_return > 0, na.rm = TRUE) * 100,
    n_years = n(),
    .groups = 'drop'
  )

# Show the most stable markets with good returns
stable_markets <- stability_metrics %>%
  filter(mean_return > 0) %>%  # Only consider markets with positive returns
  arrange(coef_variation) %>%  # Sort by stability (low coefficient of variation)
  head(5)

stable_markets %>%
  mutate(
    mean_return = sprintf("%.2f%%", mean_return),
    std_dev = sprintf("%.2f%%", std_dev),
    coef_variation = round(coef_variation, 2),  # Add coefficient of variation to output
    sharpe_ratio = round(sharpe_ratio, 3),
    pos_years_pct = sprintf("%.1f%%", pos_years_pct)
  ) %>%
  select(country, mean_return, std_dev, coef_variation, sharpe_ratio, pos_years_pct) %>%
  kable(
    caption = "Most Stable Markets for Consistent Profits",
    col.names = c("Country", "Mean Return", "Std Dev", "CoV", "Sharpe Ratio", "% Positive Years"),
    align = "lrrrrrr"
  )%>% 
    kable_styling(font_size = 24)  
```

## Highest Return Markets

```{r}
# Show the highest return markets
high_return_markets <- stability_metrics %>%
  arrange(desc(mean_return)) %>%  # Sort by return (descending)
  head(5)

high_return_markets %>%
  mutate(
    mean_return = sprintf("%.2f%%", mean_return),
    std_dev = sprintf("%.2f%%", std_dev),
    sharpe_ratio = round(sharpe_ratio, 3),
    pos_years_pct = sprintf("%.1f%%", pos_years_pct)
  ) %>%
  select(country, mean_return, std_dev, sharpe_ratio, pos_years_pct) %>%
  kable(
    caption = "Highest Return Markets",
    col.names = c("Country", "Mean Return", "Std Dev", "Sharpe Ratio", "% Positive Years"),
    align = "lrrrr"
  )%>% 
    kable_styling(font_size = 24)  
```

## Markets to Avoid

```{r}
# Show the markets to avoid
markets_to_avoid <- stability_metrics %>%
  arrange(sharpe_ratio) %>%  # Sort by Sharpe ratio (ascending)
  head(5)

markets_to_avoid %>%
  mutate(
    mean_return = sprintf("%.2f%%", mean_return),
    std_dev = sprintf("%.2f%%", std_dev),
    sharpe_ratio = round(sharpe_ratio, 3),
    pos_years_pct = sprintf("%.1f%%", pos_years_pct)
  ) %>%
  select(country, mean_return, std_dev, sharpe_ratio, pos_years_pct) %>%
  kable(
    caption = "Markets to Avoid",
    col.names = c("Country", "Mean Return", "Std Dev", "Sharpe Ratio", "% Positive Years"),
    align = "lrrrr"
  )%>% 
    kable_styling(font_size = 24)  
```

## Regional Attractiveness

```{r}
# Compare regions
regional_metrics %>%
  filter(benchmark %in% c("Asia8", "Euro7")) %>%
  mutate(
    mean_return = sprintf("%.2f%%", mean_return),
    median_return = sprintf("%.2f%%", median_return),
    std_dev = sprintf("%.2f%%", std_dev),
    sharpe_ratio = round(sharpe_ratio, 3),
    pos_years_pct = sprintf("%.1f%%", pos_years_pct),
    outperformance_rate = sprintf("%.1f%%", outperformance_rate)
  ) %>%
  kable(
    caption = "Attractiveness by Region",
    col.names = c("Region", "Mean Return", "Median Return", "Std Dev", "Sharpe Ratio", 
                  "% Positive Years", "% Outperformance"),
    align = "lrrrrrr"
  ) %>% 
    kable_styling(font_size = 24)  

```

## Investment Recommendations {.section .center}

Based on our comprehensive analysis, we recommend:

**For stable returns**: Focus on India, Indonesia, and Singapore

Best combination of stability and consistent profits

**For growth investors**: Consider India, Indonesia, and Germany

Highest average returns with acceptable risk profiles

**Markets to avoid**: Italy, Spain, and France

Poor risk-adjusted returns and inconsistent performance

## Regional allocation {.center}

-  **Asia**: Higher returns with greater volatility (growth-oriented
investors) 
-  **Europe**: More consistent performance (conservative
investors)

## Optimal Portfolio Strategy {.center}
Recommended Allocation

-  Core (50%): India, Indonesia, Singapore 
-  Growth (30%): Add Germany
-  Diversification (20%): Select Netherlands Avoid: Italy, Spain, France



## Note {.center}
This is a conceptual portfolio allocation based on the findings.
Actual allocations should be customized based on investor risk
profile and investment goals. 


# Thank You {.center}
